---
title:
  Full ICS report of presenting complaints in primary care that could be addressed through Personalised Care
header-includes:
   -  \usepackage[default]{sourcesanspro}
   -  \usepackage[T1]{fontenc}
   -  \usepackage{fancyhdr}
   - \pagestyle{fancy}
   - \addtolength{\headheight}{1.0cm} % make more space for the header
   - \pagestyle{fancyplain} % use fancy for all pages except chapter start
   - \rhead{\includegraphics[height=1.0cm]{RCGP_RSC.jpg}}
   - \chead{\includegraphics[height=1.0cm]{orchid-logo-04032021.jpg}}
   - \lhead{\includegraphics[height=1.0cm]{univ-oxford-logo.PNG}}
   - \renewcommand{\headrulewidth}{0.4pt}
   - \renewcommand{\footrulewidth}{0.4pt}
mainfont: SourceSansPro
author: ""
date: ""
output: pdf_document

params:
  ics: default

---

---
subtitle: `r params$ics`
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE,fig.align = "center",  dev="cairo_pdf")
knitr::opts_chunk$set(echo = FALSE,
                        fig.width = 6,
                        fig.asp = 0.7,
                        out.width = "80%", 
                        dev="cairo_pdf",
                        warning = FALSE, 
                        message = FALSE)
```




```{r, include=FALSE}
source("ics-data-v2.R", local = knitr::knit_global())
library(reshape2)

##Set ICS
ics = params$ics

## Custom theme  for visualisations

theme_sp <- function(base_size = 14) {
  theme_bw(base_size = base_size) %+replace%
    theme(
      # L'ensemble de la figure
      plot.title = element_text(size = rel(1), face = "bold", margin = margin(0,0,5,0), hjust = 0),
      # Zone où se situe le graphique
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      # Les axes
      axis.title = element_text(size = rel(0.85), face = "bold"),
      axis.text = element_text(size = rel(0.70), face = "bold"),
      axis.line = element_line(color = "black", arrow = arrow(length = unit(0.3, "lines"), type = "closed")),
      # La légende
      legend.title = element_text(size = rel(0.85), face = "bold"),
      legend.text = element_text(size = rel(0.70), face = "bold"),
      legend.key = element_rect(fill = "transparent", colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", colour = NA),
      # Les étiquettes dans le cas d'un facetting
      strip.background = element_rect(fill = "#17252D", color = "#17252D"),
      strip.text = element_text(size = rel(0.85), face = "bold", color = "white", margin = margin(5,0,5,0))
    )
}


```

It is well established that 80-90\% of health outcomes are linked to social determinants of health. These include health-related behaviours (e.g. tobacco use, alcohol use, diet & exercise, etc.), socioeconomic factors (e.g. education, job status, family/social support, income, etc.) and environmental factors (e.g. air quality, water quality, etc.).  It is also well established that ~20\% of patients go to their general practitioner for primarily social problems.  To define and capture social need, we used several key concepts derived from the “Five Ways to Wellbeing” model proposed by the New Economics Foundation as well as Wilkinson and Marmot’s work on social determinants of health.  Our long list included several indicators which we then checked within SNOMED to determine if concepts with appropriate semantic tags were available.  This yielded eight indicators with categories and theme variables.

To support a learning health system approach for your ICS, ORCHID has prepared the following report to provide an overview of individuals presenting to GP practices (all of which are members of the RCGP Research Surveillance Centre) within your ICS across different dimensions including: time [for the last quarter of the 2019-2020 financial year (i.e. 2019 Q4) and four quarters of the 2020-2021 financial year (i.e. 2020 Q1-Q4)]; gender; age; ethnicity; Index of Multiple Deprivation (IMD). Reference data is also presented for the Nat'l avg across all groups. 

Interactive visualisations can be found at: https://orchid.phc.ox.ac.uk/index.php/social-prescribing/ 

All ICS reports can be found at: https://orchid.phc.ox.ac.uk/index.php/social-prescribing-reports/ 

For any queries, please feel free to contact Anant Jani <anant.r.jani@gmail.com>

\textit{Acknowledgments: General Practices (all of which are members of the RCGP Research Surveillance Centre, a sentinel network of >1900 nationally representative GP practices spread across England) who volunteer to be part of the RCGP RSC network and allow us to extract and used health data for surveillance, quality improvement and research. Patients for allowing their data to be used for surveillance and research.The funding for this project was provided by NHS-E. }

\textit{ NB:For low numbers of events (as indicated by low rates per 10,000 - the numbers on the vertical/y-axis), it is important to note that the data does not represent a large enough sample size to draw meaningful conclusions apart from the fact that there is very little activity happening in these areas.}

\center{
Data source: Oxford-RCGP Clinical Informatics Digital Hub (ORCHID) (https://orchid.phc.ox.ac.uk/) / [RCGP RSC](https://www.rcgp.org.uk/clinical-and-research/our-programmes/research-and-surveillance-centre.aspx)

}



## Issues relating to mental health
```{r socialneed-mentalhealth}

    dfSocialNeed<-as.data.frame(mergedSociaNeed)
    df1 <- dfSocialNeed %>%
      filter(ics_name==ics) %>%
      select(qtr, mean_mh_rate, nat_mean_mh_rate)
    df2 <- melt(df1, id.vars = 'qtr')
    
   ggplot(df2, aes(x=qtr, y=value, fill=variable)) +
      geom_bar(stat='identity', position='dodge') +
      theme_sp() +
      xlab("Financial Quarter") +
      ylab("Issues relating to mental health/ 10,000")+
      guides(fill=guide_legend(title=""))+
      scale_fill_discrete(labels = c("ICS", "National"))+
      scale_x_yearqtr(breaks = seq(from = min(df2$qtr), to = max(df2$qtr), by = 0.25),
                      format = "%Y Q%q")  +
      theme(axis.text.x = element_text(angle = 90, hjust=1))


```

## Issues related to mental health - Age groups

```{r mentalhealth-agegroups}

dfNationalRate <-dfNationalMean_socialneed%>% 
                          mutate(cat_val="National") %>% 
                          select(qtr,cat_val, nat_mean_mh_rate) %>% 
                          rename(mh_rate = nat_mean_mh_rate)

df1<-dfICSReport_CD %>% 
  filter(cat=="Age" & ics_name==ics ) %>% 
  select(qtr, cat_val,mh_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=mh_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: 1-17","ICS average: 18-39","ICS average: 40-64","ICS average: 65+", "Nat'l avg across all groups"),
                       values=c("red","green","blue","orange", "black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to mental health - Gender

```{r mentalhealth-gender}

df1<-dfICSReport_CD %>% 
  filter(cat=="Gender" & ics_name==ics ) %>% 
  select(qtr, cat_val,mh_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=mh_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Female","ICS average: Male", "Nat'l avg across all groups"),
                       values=c("red","blue","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to mental health - Ethnicity

```{r mentalhealth-ethnicity}

df1<-dfICSReport_CD %>% 
  filter(cat=="Ethnicity" & ics_name==ics ) %>% 
  select(qtr, cat_val,mh_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=mh_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Asian","ICS average: Black", "ICS average: Mixed",
                                 "Nat'l avg across all groups", "ICS average: Other", "ICS average:Unknown",
                                "ICS average: White"),
                       values=c("lightcoral","lightsalmon2","mediumseagreen","black",
                                "lightskyblue", "mediumpurple", "maroon3"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to mental health - Index of Multiple Deprivation (IMD)

```{r mentalhealth-IMD}

df1<-dfICSReport_CD %>% 
  filter(cat=="IMD" & ics_name==ics ) %>% 
  select(qtr, cat_val,mh_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=mh_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: IMD=1","ICS average: IMD=2", "ICS average: IMD=3",
                                 "ICS average: IMD=4", "ICS average: IMD=5","Nat'l avg across all groups"),
                       values=c("lightsalmon2","mediumseagreen", "lightskyblue", "mediumpurple", "maroon3","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

\newpage

## Issues relating to substance misuse
```{r socialneed-substance-misuse}

   dfSocialNeed<-as.data.frame(mergedSociaNeed)
   df1 <- dfSocialNeed %>%
      filter(ics_name==ics) %>%
      select(qtr, mean_subst_rate, nat_mean_subst_rate)
   df2 <- melt(df1, id.vars = 'qtr')
  
  ggplot(df2, aes(x=qtr, y=value, fill=variable)) +
      geom_bar(stat='identity', position='dodge') +
      theme_sp() +
      xlab("Financial Quarter") +
      ylab("Mean weekly rate/10,000")+
      guides(fill=guide_legend(title=""))+
      scale_fill_discrete(labels = c("ICS", "National"))+
      scale_x_yearqtr(breaks = seq(from = min(df2$qtr), to = max(df2$qtr), by = 0.25), format = "%Y Q%q")  +
      theme(axis.text.x = element_text(angle = 90, hjust=1))


```

## Issues related to substance misuse - Age groups

```{r substanceabuse-agegroups}

dfNationalRate <-dfNationalMean_socialneed%>% 
                          mutate(cat_val="National") %>% 
                          select(qtr,cat_val, nat_mean_subst_rate) %>% 
                          rename(subst_rate = nat_mean_subst_rate)

df1<-dfICSReport_CD %>% 
  filter(cat=="Age" & ics_name==ics ) %>% 
  select(qtr, cat_val,subst_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=subst_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: 1-17","ICS average: 18-39","ICS average: 40-64","ICS average: 65+", "Nat'l avg across all groups"),
                       values=c("red","green","blue","orange", "black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to substance misuse - Gender

```{r substanceabuse-gender}

df1<-dfICSReport_CD %>% 
  filter(cat=="Gender" & ics_name==ics ) %>% 
  select(qtr, cat_val,subst_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=subst_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Female","ICS average: Male", "Nat'l avg across all groups"),
                       values=c("red","blue","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to substance misuse - Ethnicity

```{r substanceabuse-ethnicity}

df1<-dfICSReport_CD %>% 
  filter(cat=="Ethnicity" & ics_name==ics ) %>% 
  select(qtr, cat_val,subst_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=subst_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Asian","ICS average: Black", "ICS average: Mixed",
                                 "Nat'l avg across all groups", "ICS average: Other", "ICS average:Unknown",
                                "ICS average: White"),
                       values=c("lightcoral","lightsalmon2","mediumseagreen","black",
                                "lightskyblue", "mediumpurple", "maroon3"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to substance misuse - Index of Multiple Deprivation (IMD)

```{r substanceabuse-IMD}

df1<-dfICSReport_CD %>% 
  filter(cat=="IMD" & ics_name==ics ) %>% 
  select(qtr, cat_val,subst_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=subst_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: IMD=1","ICS average: IMD=2", "ICS average: IMD=3",
                                 "ICS average: IMD=4", "ICS average: IMD=5","Nat'l avg across all groups"),
                       values=c("lightsalmon2","mediumseagreen", "lightskyblue", "mediumpurple", "maroon3","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```
\newpage


## Issues relating to employment
```{r socialneed-employment}

  dfSocialNeed<-as.data.frame(mergedSociaNeed)
  df1 <- dfSocialNeed %>%
    filter(ics_name==ics) %>%
    select(qtr, mean_empl_rate, nat_mean_empl_rate)
  df2 <- melt(df1, id.vars = 'qtr')
 
  ggplot(df2, aes(x=qtr, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
  guides(fill=guide_legend(title=""))+
  scale_fill_discrete(labels = c("ICS", "National"))+
  scale_x_yearqtr(breaks = seq(from = min(df2$qtr), to = max(df2$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))


```

## Issues related to employment- Age groups

```{r employment-agegroups}

dfNationalRate <-dfNationalMean_socialneed%>% 
                          mutate(cat_val="National") %>% 
                          select(qtr,cat_val, nat_mean_empl_rate) %>% 
                          rename(empl_rate = nat_mean_empl_rate)

df1<-dfICSReport_CD %>% 
  filter(cat=="Age" & ics_name==ics ) %>% 
  select(qtr, cat_val,empl_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=empl_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: 1-17","ICS average: 18-39","ICS average: 40-64","ICS average: 65+", "Nat'l avg across all groups"),
                       values=c("red","green","blue","orange", "black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to employment - Gender

```{r employment-gender}

df1<-dfICSReport_CD %>% 
  filter(cat=="Gender" & ics_name==ics ) %>% 
  select(qtr, cat_val,empl_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=empl_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Female","ICS average: Male", "Nat'l avg across all groups"),
                       values=c("red","blue","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to employment - Ethnicity

```{r employment-ethnicity}

df1<-dfICSReport_CD %>% 
  filter(cat=="Ethnicity" & ics_name==ics ) %>% 
  select(qtr, cat_val,empl_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=empl_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Asian","ICS average: Black", "ICS average: Mixed",
                                 "Nat'l avg across all groups", "ICS average: Other", "ICS average:Unknown",
                                "ICS average: White"),
                       values=c("lightcoral","lightsalmon2","mediumseagreen","black",
                                "lightskyblue", "mediumpurple", "maroon3"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to employment - Index of Multiple Deprivation (IMD)

```{r employment-IMD}

df1<-dfICSReport_CD %>% 
  filter(cat=="IMD" & ics_name==ics ) %>% 
  select(qtr, cat_val,empl_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=empl_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: IMD=1","ICS average: IMD=2", "ICS average: IMD=3",
                                 "ICS average: IMD=4", "ICS average: IMD=5","Nat'l avg across all groups"),
                       values=c("lightsalmon2","mediumseagreen", "lightskyblue", "mediumpurple", "maroon3","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

\newpage

## Issues relating to money

```{r socialneed-money}

  dfSocialNeed<-as.data.frame(mergedSociaNeed)
  df1 <- dfSocialNeed %>%
    filter(ics_name==ics) %>%
    select(qtr, mean_money_rate, nat_mean_money_rate)
  df2 <- melt(df1, id.vars = 'qtr')
  
  ggplot(df2, aes(x=qtr, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
  guides(fill=guide_legend(title=""))+
  scale_fill_discrete(labels = c("ICS", "National"))+
  scale_x_yearqtr(breaks = seq(from = min(df2$qtr), to = max(df2$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related to money - Age groups

```{r money-agegroups}

dfNationalRate <-dfNationalMean_socialneed%>% 
                          mutate(cat_val="National") %>% 
                          select(qtr,cat_val, nat_mean_money_rate) %>% 
                          rename(money_rate = nat_mean_money_rate)

df1<-dfICSReport_CD %>% 
  filter(cat=="Age" & ics_name==ics ) %>% 
  select(qtr, cat_val,money_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=money_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: 1-17","ICS average: 18-39","ICS average: 40-64","ICS average: 65+", "Nat'l avg across all groups"),
                       values=c("red","green","blue","orange", "black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to money - Gender

```{r money-gender}

df1<-dfICSReport_CD %>% 
  filter(cat=="Gender" & ics_name==ics ) %>% 
  select(qtr, cat_val,money_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=money_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Female","ICS average: Male", "Nat'l avg across all groups"),
                       values=c("red","blue","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to money - Ethnicity

```{r money-ethnicity}

df1<-dfICSReport_CD %>% 
  filter(cat=="Ethnicity" & ics_name==ics ) %>% 
  select(qtr, cat_val,money_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=money_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Asian","ICS average: Black", "ICS average: Mixed",
                                 "Nat'l avg across all groups", "ICS average: Other", "ICS average:Unknown",
                                "ICS average: White"),
                       values=c("lightcoral","lightsalmon2","mediumseagreen","black",
                                "lightskyblue", "mediumpurple", "maroon3"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues relating to money - Index of Multiple Deprivation (IMD)

```{r money-IMD}

df1<-dfICSReport_CD %>% 
  filter(cat=="IMD" & ics_name==ics ) %>% 
  select(qtr, cat_val,money_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=money_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: IMD=1","ICS average: IMD=2", "ICS average: IMD=3",
                                 "ICS average: IMD=4", "ICS average: IMD=5","Nat'l avg across all groups"),
                       values=c("lightsalmon2","mediumseagreen", "lightskyblue", "mediumpurple", "maroon3","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

\newpage

## Issues relating to managing a long term condition
```{r socialneed-ltc}

  dfSocialNeed<-as.data.frame(mergedSociaNeed)
  df1 <- dfSocialNeed %>%
    filter(ics_name==ics) %>%
    select(qtr, mean_ltc_rate, nat_mean_ltc_rate)
  df2 <- melt(df1, id.vars = 'qtr')
  ggplot(df2, aes(x=qtr, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge') +
    theme_sp() +
    xlab("Financial Quarter") +
    ylab("Mean weekly rate/10,000")+
    guides(fill=guide_legend(title=""))+
    scale_fill_discrete(labels = c("ICS", "National"))+
    scale_x_yearqtr(breaks = seq(from = min(df2$qtr), to = max(df2$qtr), by = 0.25),
                    format = "%Y Q%q")  +
    theme(axis.text.x = element_text(angle = 90, hjust=1))


```

## Issues related to a long term condition - Age groups

```{r ltc-agegroups}

dfNationalRate <-dfNationalMean_socialneed%>% 
                          mutate(cat_val="National") %>% 
                          select(qtr,cat_val, nat_mean_ltc_rate) %>% 
                          rename(ltc_rate = nat_mean_ltc_rate)

df1<-dfICSReport_CD %>% 
  filter(cat=="Age" & ics_name==ics ) %>% 
  select(qtr, cat_val,ltc_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=ltc_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: 1-17","ICS average: 18-39","ICS average: 40-64","ICS average: 65+", "Nat'l avg across all groups"),
                       values=c("red","green","blue","orange", "black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related to a long term condition - Gender

```{r ltc-gender}

df1<-dfICSReport_CD %>% 
  filter(cat=="Gender" & ics_name==ics ) %>% 
  select(qtr, cat_val,ltc_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=ltc_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Female","ICS average: Male", "Nat'l avg across all groups"),
                       values=c("red","blue","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related to a long term condition - Ethnicity

```{r ltc-ethnicity}

df1<-dfICSReport_CD %>% 
  filter(cat=="Ethnicity" & ics_name==ics ) %>% 
  select(qtr, cat_val,ltc_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=ltc_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Asian","ICS average: Black", "ICS average: Mixed",
                                 "Nat'l avg across all groups", "ICS average: Other", "ICS average:Unknown",
                                "ICS average: White"),
                       values=c("lightcoral","lightsalmon2","mediumseagreen","black",
                                "lightskyblue", "mediumpurple", "maroon3"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related to a long term condition - Index of Multiple Deprivation (IMD)

```{r ltc-IMD}

df1<-dfICSReport_CD %>% 
  filter(cat=="IMD" & ics_name==ics ) %>% 
  select(qtr, cat_val,ltc_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=ltc_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: IMD=1","ICS average: IMD=2", "ICS average: IMD=3",
                                 "ICS average: IMD=4", "ICS average: IMD=5","Nat'l avg across all groups"),
                       values=c("lightsalmon2","mediumseagreen", "lightskyblue", "mediumpurple", "maroon3","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```
\newpage

## Issues relating to abuse
```{r socialneed-abuse}

  dfSocialNeed<-as.data.frame(mergedSociaNeed)
  df1 <- dfSocialNeed %>%
    filter(ics_name==ics) %>%
    select(qtr, mean_abuse_rate, nat_mean_abuse_rate)
  df2 <- melt(df1, id.vars = 'qtr')
  ggplot(df2, aes(x=qtr, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge') +
    theme_sp() +
    xlab("Financial Quarter") +
    ylab("Mean weekly rate/10,000")+
    guides(fill=guide_legend(title=""))+
    scale_fill_discrete(labels = c("ICS", "National"))+
    scale_x_yearqtr(breaks = seq(from = min(df2$qtr), to = max(df2$qtr), by = 0.25),
                    format = "%Y Q%q")  +
    theme(axis.text.x = element_text(angle = 90, hjust=1))


```

## Issues related to abuse - Age groups

```{r abuse-agegroups}

dfNationalRate <-dfNationalMean_socialneed%>% 
                          mutate(cat_val="National") %>% 
                          select(qtr,cat_val, nat_mean_abuse_rate) %>% 
                          rename(abuse_rate = nat_mean_abuse_rate)

df1<-dfICSReport_CD %>% 
  filter(cat=="Age" & ics_name==ics ) %>% 
  select(qtr, cat_val,abuse_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=abuse_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: 1-17","ICS average: 18-39","ICS average: 40-64","ICS average: 65+", "Nat'l avg across all groups"),
                       values=c("red","green","blue","orange", "black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related to abuse - Gender

```{r abuse-gender}

df1<-dfICSReport_CD %>% 
  filter(cat=="Gender" & ics_name==ics ) %>% 
  select(qtr, cat_val,abuse_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=abuse_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("IMean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Female","ICS average: Male", "Nat'l avg across all groups"),
                       values=c("red","blue","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related to abuse - Ethnicity

```{r abuse-ethnicity}

df1<-dfICSReport_CD %>% 
  filter(cat=="Ethnicity" & ics_name==ics ) %>% 
  select(qtr, cat_val,abuse_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=abuse_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Asian","ICS average: Black", "ICS average: Mixed",
                                 "Nat'l avg across all groups", "ICS average: Other", "ICS average:Unknown",
                                "ICS average: White"),
                       values=c("lightcoral","lightsalmon2","mediumseagreen","black",
                                "lightskyblue", "mediumpurple", "maroon3"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related to abuse - Index of Multiple Deprivation (IMD)

```{r abuse-IMD}

df1<-dfICSReport_CD %>% 
  filter(cat=="IMD" & ics_name==ics ) %>% 
  select(qtr, cat_val,abuse_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=abuse_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: IMD=1","ICS average: IMD=2", "ICS average: IMD=3",
                                 "ICS average: IMD=4", "ICS average: IMD=5","Nat'l avg across all groups"),
                       values=c("lightsalmon2","mediumseagreen", "lightskyblue", "mediumpurple", "maroon3","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```
\newpage

## Issues relating to housing
```{r socialneed-housing}

  dfSocialNeed<-as.data.frame(mergedSociaNeed)
  df1 <- dfSocialNeed %>%
    filter(ics_name==ics) %>%
    select(qtr, mean_housing_rate, nat_mean_housing_rate)
  df2 <- melt(df1, id.vars = 'qtr')
  ggplot(df2, aes(x=qtr, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge') +
    theme_sp() +
    xlab("Financial Quarter") +
    ylab("Mean weekly rate/10,000")+
    guides(fill=guide_legend(title=""))+
    scale_fill_discrete(labels = c("ICS", "National"))+
    scale_x_yearqtr(breaks = seq(from = min(df2$qtr), to = max(df2$qtr), by = 0.25),
                    format = "%Y Q%q")  +
    theme(axis.text.x = element_text(angle = 90, hjust=1))


```

## Issues related to housing - Age groups

```{r housing-agegroups}

dfNationalRate <-dfNationalMean_socialneed%>% 
                          mutate(cat_val="National") %>% 
                          select(qtr,cat_val, nat_mean_housing_rate) %>% 
                          rename(housing_rate = nat_mean_housing_rate)

df1<-dfICSReport_CD %>% 
  filter(cat=="Age" & ics_name==ics ) %>% 
  select(qtr, cat_val,housing_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=housing_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: 1-17","ICS average: 18-39","ICS average: 40-64","ICS average: 65+", "Nat'l avg across all groups"),
                       values=c("red","green","blue","orange", "black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related to housing - Gender

```{r housing-gender}

df1<-dfICSReport_CD %>% 
  filter(cat=="Gender" & ics_name==ics ) %>% 
  select(qtr, cat_val,housing_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=housing_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Female","ICS average: Male", "Nat'l avg across all groups"),
                       values=c("red","blue","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related to housing - Ethnicity

```{r housing-ethnicity}

df1<-dfICSReport_CD %>% 
  filter(cat=="Ethnicity" & ics_name==ics ) %>% 
  select(qtr, cat_val,housing_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=housing_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Asian","ICS average: Black", "ICS average: Mixed",
                                 "Nat'l avg across all groups", "ICS average: Other", "ICS average:Unknown",
                                "ICS average: White"),
                       values=c("lightcoral","lightsalmon2","mediumseagreen","black",
                                "lightskyblue", "mediumpurple", "maroon3"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related housing - Index of Multiple Deprivation (IMD)

```{r housing-IMD}

df1<-dfICSReport_CD %>% 
  filter(cat=="IMD" & ics_name==ics ) %>% 
  select(qtr, cat_val,housing_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=housing_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: IMD=1","ICS average: IMD=2", "ICS average: IMD=3",
                                 "ICS average: IMD=4", "ICS average: IMD=5","Nat'l avg across all groups"),
                       values=c("lightsalmon2","mediumseagreen", "lightskyblue", "mediumpurple", "maroon3","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```
\newpage

## Issues relating to parenting
```{r socialneed-parenting}

  dfSocialNeed<-as.data.frame(mergedSociaNeed)
  df1 <- dfSocialNeed %>%
    filter(ics_name==ics) %>%
    select(qtr, mean_parent_rate, nat_mean_parent_rate)
  df2 <- melt(df1, id.vars = 'qtr')
  ggplot(df2, aes(x=qtr, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge') +
    theme_sp() +
    xlab("Financial Quarter") +
    ylab("Mean weekly rate/10,000")+
    guides(fill=guide_legend(title=""))+
    scale_fill_discrete(labels = c("ICS", "National"))+
    scale_x_yearqtr(breaks = seq(from = min(df2$qtr), to = max(df2$qtr), by = 0.25),
                    format = "%Y Q%q")  +
    theme(axis.text.x = element_text(angle = 90, hjust=1))


```

## Issues related to parenting - Age groups

```{r parenting-agegroups}

dfNationalRate <-dfNationalMean_socialneed%>% 
                          mutate(cat_val="National") %>% 
                          select(qtr,cat_val, nat_mean_parent_rate) %>% 
                          rename(parent_rate = nat_mean_parent_rate)

df1<-dfICSReport_CD %>% 
  filter(cat=="Age" & ics_name==ics ) %>% 
  select(qtr, cat_val,parent_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=parent_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: 1-17","ICS average: 18-39","ICS average: 40-64","ICS average: 65+", "Nat'l avg across all groups"),
                       values=c("red","green","blue","orange", "black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related to parenting - Gender

```{r parenting-gender}

df1<-dfICSReport_CD %>% 
  filter(cat=="Gender" & ics_name==ics ) %>% 
  select(qtr, cat_val,parent_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=parent_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Female","ICS average: Male", "Nat'l avg across all groups"),
                       values=c("red","blue","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related to parenting - Ethnicity

```{r parenting-ethnicity}

df1<-dfICSReport_CD %>% 
  filter(cat=="Ethnicity" & ics_name==ics ) %>% 
  select(qtr, cat_val,parent_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=parent_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: Asian","ICS average: Black", "ICS average: Mixed",
                                 "Nat'l avg across all groups", "ICS average: Other", "ICS average:Unknown",
                                "ICS average: White"),
                       values=c("lightcoral","lightsalmon2","mediumseagreen","black",
                                "lightskyblue", "mediumpurple", "maroon3"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```

## Issues related parenting - Index of Multiple Deprivation (IMD)

```{r parenting-IMD}

df1<-dfICSReport_CD %>% 
  filter(cat=="IMD" & ics_name==ics ) %>% 
  select(qtr, cat_val,parent_rate ) %>% 
  bind_rows(.,dfNationalRate) %>% 
  group_by(cat_val)

  ggplot(df1,aes(x=qtr,y=parent_rate, group=cat_val,color=cat_val)) +
  geom_line(size=1.5) +
  theme_sp() +
  xlab("Financial Quarter") +
  ylab("Mean weekly rate/10,000")+
    theme(legend.title=element_blank())+
  scale_color_manual(labels = c("ICS average: IMD=1","ICS average: IMD=2", "ICS average: IMD=3",
                                 "ICS average: IMD=4", "ICS average: IMD=5","Nat'l avg across all groups"),
                       values=c("lightsalmon2","mediumseagreen", "lightskyblue", "mediumpurple", "maroon3","black"))+
  scale_x_yearqtr(breaks = seq(from = min(df1$qtr), to = max(df1$qtr), by = 0.25),
                  format = "%Y Q%q")  +
  theme(axis.text.x = element_text(angle = 90, hjust=1))
```


